MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-07-17 latex/paper/sections/11-placement_results.tex
more test trials

Also note the sparsity of the \texttt{DSP48E1} (yellow) and \texttt{RAMB18E1} (magenta) \texttt{Site} columns compared to the large grid of \texttt{SLICEL}s (cyan).

>>>>

Also note the sparsity of the \texttt{DSP48E1} (yellow) and \texttt{RAMB18E1} (magenta) \texttt{Site} columns compared to the more uniform grid of \texttt{SLICEL}s (cyan).
